### 2017-11-21 manuscript.rmd
ggtree colored tip label figures include=F

####Distribution of sex across siphonophore taxa
```{r ggtree_sex, echo=F, message=F, warning=F}
exp_tree = ultratree
exp_tree$edge.length = 10*ultratree$edge.length
dd = data.frame(taxa  = tree$tip.label, trait = sex[match(tree$tip.label, names(sex))])
p = ggtree(exp_tree, layout="rectangular") + xlim(NA, 23)
p = p %<+% dd + geom_tiplab(aes(color=trait), show_guide = FALSE, size = 3.5) + geom_tippoint(aes(color=trait), alpha=0.25)
p+theme(legend.position="right") + guides(color=guide_legend(title="Sex distribution", reverse=T)) 
```

####Tentilla presence across siphonophore taxa
```{r ggtree_tentillq, echo=F, message=F, warning=F}
exp_tree = ultratree
exp_tree$edge.length = 10*ultratree$edge.length
dd = data.frame(taxa  = tree$tip.label, trait = as.factor(tentilla[match(tree$tip.label, names(tentilla))]))
p = ggtree(exp_tree, layout="rectangular") + xlim(NA, 23)
p = p %<+% dd + geom_tiplab(aes(color=trait), show_guide = FALSE, size = 3.5) + geom_tippoint(aes(color=trait), alpha=0.25)
p+theme(legend.position="right") + guides(color=guide_legend(title="Tentilla", reverse=T)) 
```

####Palpon presence across siphonophore taxa
```{r ggtree_palpon, echo=F, message=F, warning=F}
exp_tree = ultratree
exp_tree$edge.length = 10*ultratree$edge.length
dd = data.frame(taxa  = tree$tip.label, trait = as.factor(palpons[match(tree$tip.label, names(palpons))]))
p = ggtree(exp_tree, layout="rectangular") + xlim(NA, 23)
p = p %<+% dd + geom_tiplab(aes(color=trait), show_guide = FALSE, size = 3.5) + geom_tippoint(aes(color=trait), alpha=0.25)
p+theme(legend.position="right") + guides(color=guide_legend(title="Palpons", reverse=T)) 
```

>>>>

####Distribution of sex across siphonophore taxa
```{r ggtree_sex, echo=F, message=F, warning=F, include=F}
exp_tree = ultratree
exp_tree$edge.length = 10*ultratree$edge.length
dd = data.frame(taxa  = tree$tip.label, trait = sex[match(tree$tip.label, names(sex))])
p = ggtree(exp_tree, layout="rectangular") + xlim(NA, 23)
p = p %<+% dd + geom_tiplab(aes(color=trait), show_guide = FALSE, size = 3.5) + geom_tippoint(aes(color=trait), alpha=0.25)
p+theme(legend.position="right") + guides(color=guide_legend(title="Sex distribution", reverse=T)) 
```

####Tentilla presence across siphonophore taxa
```{r ggtree_tentillq, echo=F, message=F, warning=F, include=F}
exp_tree = ultratree
exp_tree$edge.length = 10*ultratree$edge.length
dd = data.frame(taxa  = tree$tip.label, trait = as.factor(tentilla[match(tree$tip.label, names(tentilla))]))
p = ggtree(exp_tree, layout="rectangular") + xlim(NA, 23)
p = p %<+% dd + geom_tiplab(aes(color=trait), show_guide = FALSE, size = 3.5) + geom_tippoint(aes(color=trait), alpha=0.25)
p+theme(legend.position="right") + guides(color=guide_legend(title="Tentilla", reverse=T)) 
```

####Palpon presence across siphonophore taxa
```{r ggtree_palpon, echo=F, message=F, warning=F, include=F}
exp_tree = ultratree
exp_tree$edge.length = 10*ultratree$edge.length
dd = data.frame(taxa  = tree$tip.label, trait = as.factor(palpons[match(tree$tip.label, names(palpons))]))
p = ggtree(exp_tree, layout="rectangular") + xlim(NA, 23)
p = p %<+% dd + geom_tiplab(aes(color=trait), show_guide = FALSE, size = 3.5) + geom_tippoint(aes(color=trait), alpha=0.25)
p+theme(legend.position="right") + guides(color=guide_legend(title="Palpons", reverse=T)) 
```
